### 2023-05-26 state-resilience.tex
sections

\begin{theorem}[Adjusting Theorem~5.5 from \cite{peterson1981petri}]\label{liveness reset}
The  zero reachability problem can be reduced to the $t$-liveness problem in Reset VASS.
\end{theorem}

@@

Keeping the $\uparrow \post^*$ effectiveness hypothesis but loosening the strong compatibility one still yields some decidability result for the general {\sc State-resilience }.

\begin{theorem}{(Adjusting Theorem 1 from \cite{DBLP:journals/corr/abs-2108-00889})}\label{post srp}
{\sc State-resilience} is decidable for 
%(not necessarily strong)
 WSTS with effective 
$\uparrow$ $\post^*$ basis
when
$\Safe=\uparrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\begin{proposition}\label{downward brp}
{\sc $k$-state-resilience} and {\sc bounded-state-resilience} are decidable for ideal effective WSTS with strong downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{proposition}

>>>>

\begin{proposition}[Adjusting Theorem~5.5 from \cite{peterson1981petri}]\label{liveness reset}
The  zero reachability problem can be reduced to the $t$-liveness problem in Reset VASS.
\end{proposition}

@@

Keeping the $\uparrow \post^*$ effectiveness hypothesis but loosening the strong compatibility one still yields some decidability result for the general {\sc State-resilience }. Adjusting Theorem 1 from \cite{DBLP:journals/corr/abs-2108-00889}:

\begin{theorem}\label{post srp}
{\sc State-resilience} is decidable for 
%(not necessarily strong)
 WSTS with effective 
$\uparrow$ $\post^*$ basis
when
$\Safe=\uparrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\begin{corollary}\label{downward brp}
{\sc $k$-state-resilience} and {\sc bounded-state-resilience} are decidable for ideal effective WSTS with strong downward compatibility,
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.
\end{corollary}
